### 2016-09-22 supplement.tex
Grammar

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section \ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections \ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section \ref{suppsec:numsimpl}
discusses numerical simplification.  Section \ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In sections
\ref{sympy-gamma} and \ref{sympy-live} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section \ref{comp-mma} do
brief comparison of the SymPy with the Wolfram Mathematica and the
section \ref{other-proj} lists some projects that depend on SymPy.

>>>>

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section \ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections \ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section \ref{suppsec:numsimpl}
discusses numerical simplification.  Section \ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In sections
\ref{sympy-gamma} and \ref{sympy-live} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section \ref{comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica, and
section \ref{other-proj} lists some projects that depend on SymPy.
